Expert-In-The-Loop Causal Discovery: \\ Iterative Model Refinement Using Expert Knowledge

### 2025-02-11 paper/main.tex
UPdates

Polyserial (for continuous $Y$) and polychoric
(ordinal $Y$) correlations are used to estimate correlations 
involving ordinal variables \citep{Poon1987}. Both methods make the assumption that the
observed ordinal variable is a result of thresholding a latent normally
distributed continuous variable. Under this assumption, the methods then 
estimate the threshold values and covariance matrix using maximum likelihood.
Using the estimated covariance matrix, $ \Sigma $ we can perform a correlation
test for CI and compute the Pearson's correlation coefficient as the effect
size in the same way as for continuous $ X, Y $ and $ \bm{Z} $, i.e., 
$\bm{Z} = \emptyset $, $ r_{X, Y} = \Sigma_{XY} / (\sqrt{\Sigma_{XX} \Sigma_{YY}}) $, 
	and when $ \bm{Z} \ne \emptyset $,
	$ r_{X, Y \rvert \bm{Z}} = - \Sigma^{-1}_{XY}/ (\sqrt{\Sigma^{-1}_{XX} \Sigma^{-1}_{YY}}) $.

>>>>

Polyserial (for continuous $Y$) and polychoric
(ordinal $Y$) correlations are used to estimate correlations 
involving ordinal variables \citep{Poon1987}. Both methods make the assumption that the
observed ordinal variable is a result of thresholding a latent normally
distributed continuous variable. Under this assumption, the methods then 
estimate the threshold values and covariance matrix using maximum likelihood.
Using the estimated covariance matrix, $ \Sigma $ we can perform a correlation
test for CI and compute the Pearson's correlation coefficient as the effect
size (same as for continuous $ X $ and $ Y $), i.e., 
$\bm{Z} = \emptyset $, $ r_{X, Y} = \Sigma_{XY} / (\sqrt{\Sigma_{XX} \Sigma_{YY}}) $, 
	and when $ \bm{Z} \ne \emptyset $,
	$ r_{X, Y \rvert \bm{Z}} = - \Sigma^{-1}_{XY}/ (\sqrt{\Sigma^{-1}_{XX} \Sigma^{-1}_{YY}}) $.
